\subsection{Latihan Soal Relasi Rekurensi}
\begin{enumerate}
    \item (British) Isaac is planning a nine-day holiday. Every day he will go surfing, or water skiing, or he will rest. On any given day he does just one of these three things. He never does different water-sports on consecutive days. How many schedules are possible for the holiday?

    \item (AIME I 2006) A collection of 8 cubes consists of one cube with edge-length $k$ for each integer $k, 1 \le k \le 8.$ A tower is to be built using all 8 cubes according to the rules:
    \begin{itemize}
        \item Any cube may be the bottom cube in the tower.
        \item The cube immediately on top of a cube with edge-length $k$ must have edge-length at most $k+2.$
    \end{itemize}
    Let $T$ be the number of different towers than can be constructed. What is the remainder when $T$ is divided by 1000?

    \item (AIME I 2006) For each even positive integer $x$, let $g(x)$ denote the greatest power of 2 that divides $x.$ For example, $g(20)=4$ and $g(16)=16.$ For each positive integer $n,$ let $S_n=\sum_{k=1}^{2^{n-1}}g(2k).$ Find the greatest integer $n$ less than 1000 such that $S_n$ is a perfect square.

    \item (AIME I 2001) A mail carrier delivers mail to the nineteen houses on the east side of Elm Street. The carrier notices that no two adjacent houses ever get mail on the same day, but that there are never more than two houses in a row that get no mail on the same day. How many different patterns of mail delivery are possible?
\end{enumerate}